Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-01-13 Manuscript/HI_Model_ms.Rmd
updated manuscript files

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@friedlingstein_global_2019]. There is increasing recognition among policymakers that natural and angricultural ecosystems can contribute to climate mitigation, which has given rise to the popularity of “natural carbon solutions” [@cameron_ecosystem_2017]. Natural climate solutions, defined as conservation and land management efforts aimed at enhancing ecosystem carbon storage [@griscom_natural_2017], are appealing because they are seen as cost-effective and readily available [@averchenkova_climate_2017; @cameron_ecosystem_2017; @fargione_natural_2018]. A growing number of sub-national jurisdictions plan to incorporate natural climate solutions as part of a suite of emissions reduction efforts to achieve carbon neutrality by mid-century. However, uncertainty surrounding the future direction and magnitude of the land carbon sink, especially at the regional scale, complicates efforts to effectively implement natural climate solutions.

Interannual variability in climate, land use, and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017].

>>>>

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis and reducing the rate of increase in atmospheric CO~2~ [@keenan_terrestrial_2018; @friedlingstein_global_2019]. There is increasing recognition among policymakers that natural and angricultural ecosystems can contribute to climate mitigation, which has given rise to the popularity of “natural carbon solutions” [@cameron_ecosystem_2017]. Defined as conservation and land management efforts aimed at enhancing ecosystem carbon storage [@griscom_natural_2017], natural climate solutions are appealing because they are seen as cost-effective and readily available [@averchenkova_climate_2017; @cameron_ecosystem_2017; @fargione_natural_2018]. A growing number of sub-national jurisdictions have incorporated  as part of a suite of emissions reduction efforts to achieve carbon neutrality. However, effective implementation is complicated by the uncertainty surrounding the future direction and magnitude of the land carbon sink, especially at the regional scale.

Interannual fluctuations in carbon uptake by land ecosystems is the primary driver of year-to-year variation in atmosphereric CO~2~ growth rate
Interannual variability in climate, land use, and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017].
